Discussion

### 2020-03-16 doc/Discussion.rmd
notes on discussion

---
title: "Discussion"
author: "April Peterson"
date: "March 10, 2020"
output: html_document
---

@@

This section refers to the matrix of models and results from this study where we (conceptually test if each model would support our results)

We were motivated to run a comparison of

_Models_

## 1.Gamete selection
The process where gametes are competing - so there is stronger selection for 1 form of gamete vs the other (stronger directional selection) (the gamete with more competition / the sex with more variance in reproductive fitness will have lower overall recombination rate.

@@

##2.SACE
Extension of reduction principle. Results in large blocks of genetic areas being kept together in male meiosis.

@@

This new model has _strengths_

@@

##3.Two-locus (protect for drivers)

@@

_model basics_

@@

_strengths_

@@

_weaknesses_
(modifers - driver systems everywhere!), impossible to verify, doesn't account for male landscape pattern (supression from centromere to end)

## 4. Spindle   // Difference in acentromeric spindle and SAC

@@

we like this model because it can be applied to _both our results_ for i) sexual dimorphism variation and ii) the fast male evolution in gwRR and recombination landscape.

for the distinct _evolutionary patterns_ selection on the recombination landscape via the spindle (segregation checkpoint),

@@

@@

## notes for Wu thesis
bivalent orientation early metaphase -- search and capture model -- when there are mulitple KT-MT attachmments, (lateral (on the side or not on centromere/KT proper), merotelic MT attachemtn from ooposite poles) and amplitelic (MT from same pole)
then biorientation process starts, --search and capature process (only amplictic Mt-KT attachments get stablize)

@@

-  more attention to cell physiology

>>>>

---
title: "Discussion"
date: ""
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: refs_Main_Report.bib
---

@@

This section refers to the matrix of models and results from this study where we (conceptually test if each model would support our results). We were motivated to run a comparison of

## 1.Gamete selection

The process where gametes are competing - so there is stronger selection for 1 form of gamete vs the other (stronger directional selection) (the gamete with more competition / the sex with more variance in reproductive fitness will have lower overall recombination rate.

@@

## 2. SACE

Extension of reduction principle. Results in large blocks of genetic areas being kept together in male meiosis.

@@

This new model has **strengths**

@@

## 3.Two-locus (protect for drivers)

@@

**model basics**

@@

**strengths**

@@

**weaknesses**

(modifers - driver systems everywhere!), impossible to verify, doesn't account for male landscape pattern (supression from centromere to end)

## 4. Segregation and physiological Spindle Differences

### The CONTEXT of MEIOSIS

the study confirmed preivously identified sexual dimorhisc patterns in regard to the recombiantion landscape (in mammals) -- in the goal of unifying all of these results, we sough to investigate physiologycal aspects of gametogenesis which have conserved sexual dimorphic features.

LOOK at the oogenesis and spermatogenesis as the context for meiosis (and how )

lead us to ask, how the different contexts of meiosis could influence recombination rates (the recombinaiton landscape)

(not sex chromosome)

while there are many different forms, flavors of anisogamy (cite that one paper)

symetrical vs asymetrical gamete division

@@

@@

### CO placement translates to bivalent shape

**still an open question of if and how the CO number and placement of crossovers translates to different fitness values for segregation rates**

the metric / amout of sister cohesion might be an good place to start

the ultimate goal is proper disjunction of chromosomes, the main checkpoint is spindle assembly checkpoint (SAC) which responds to the tension signal across chiasmata

we like this model because it can be applied to **both our results** for i) sexual dimorphism variation and ii) the fast male evolution in gwRR and recombination landscape.

Uses / centers around one of the best known selection factors on meiotic division, anneuploidy. Several other facors related to meiotic recombiniation center on **segregation** (obligate chiasmata, lower bound of the genome wide rate) it's not unbelievable that the recombination

for the distinct **evolutionary patterns** selection on the recombination landscape via the spindle (segregation checkpoint),

@@

#### notes for Wu thesis
bivalent orientation early metaphase -- search and capture model -- when there are mulitple KT-MT attachmments, (lateral (on the side or not on centromere/KT proper), merotelic MT attachemtn from ooposite poles) and amplitelic (MT from same pole)
then biorientation process starts, --search and capature process (only amplictic Mt-KT attachments get stablize)

@@

-  more attention to cell physiology and biophysics (conserved nature of meiosis pathway (and mitosis ) -- use some models such as Sc for manipulation) (Murkarjee gardner -- quantify the spindle tension
